---
title: 'STAT/CSSS 564: Assignment 5'
author: Jeff Arnold & Sheridan Grant
bibliography: assignment5.bib
output:
  html_document:
    toc: false
    number_sections: true
  pdf_document:
    toc: false
    number_sections: true    
---

```{r include=FALSE}
knitr::opts_chunk$set(cache = TRUE, autodep = TRUE)
```

**WORK IN PROGRESS**

# Instructions {-}

This repository contains the assignment instructions.
Submitted solutions will use a **separate** repository.

1. Fork [UW-CSSS-564/assignment-2017-5-submissions](https://github.com/UW-CSSS-564/assignment-2017-5-submissions) repository to your account.
2. Edit the file `README.Rmd` with your solutions to the problems.
3. Submit a pull request to have it graded. Include either or both a HTML and PDF file.

For updates and questions follow the Slack channel: [#assignment5](https://uwcsss564.slack.com/messages/C5DBV8266).

This assignment will require the following R packages:
```{r, message=FALSE}
library("rstan")
library("rstanarm")
library("haven")
library("tidyverse")
library("loo")
```

Set the following options for faster sampling sampling.[^rprofile]
This option sets the default to save a compiled model to disk and reuse it if the code hasn't changed.
This will avoid needless recompilation.
```{r}
rstan_options(auto_write = TRUE)
```
If you sample with multiple chains and your computer has multiple cores, this will run the chains in parallel.
```{r}
options(mc.cores = parallel::detectCores())
```
**WARNING** This will increase the amount of memory used, so if your computer does not have multiple cores, or is not powerful, you may not want to use this.
Sampling will take longer, but use less memory.


TODO


# References {-}
